A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data

### 2023-07-31 tidyindex.qmd
Update Intro paragraph 3

To be able to test different decision choices systematically for an index, the index needs to be broken down into its fundamental building blocks to analyse the effect of each component. Such decomposition of indexes standardise the index construction pipeline and offers benefit for comparing among indexes and calculate index uncertainty. In social indexes, the OECD handbook [@oecd_handbook_2008] has provided a set of steps for constructing composite socio-economic indexes, but there is a need to extend these guidelines to accommodate more complex construction steps required for indexes in general.

>>>>

To be able to test different decision choices systematically for an index, the index needs to be broken down into its fundamental building blocks to analyse the contribution and effect of each component. Such decomposition of index components provides the means to standardise index construction via a pipeline and offers benefits for comparing among indexes and calculating index uncertainty. In social indexes for instance, the OECD handbook [@oecd_handbook_2008] has provided a set of steps and recommendations for constructing composite socio-economic indexes. However, there is still a need to extend these guidelines and methods to accommodate the inclusion of more methodological complex steps required for indexes in general.
